Balsa: A Compact Line Notation Based on SMILES

### 2022-06-25 manuscript.tex
Adds figure for selection and deselction. closes #4 #5

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Deselection. Unsetting the atomic selected flag with simultaneous promotion of matching bonds.}
    \label{fig:deselection}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Selection Algorithm. Those atoms with bonds contributing to DIME are added to the delocalization subgraph.}
    \label{fig:selection}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{selection-and-deselection.pdf}
    \caption{Deselection and Selection. Deselection unsets the atomic selected flag with simultaneous promotion of matching bonds. Selection sets the atomic selected flag with simultaneous demotion of intervening single and double bonds to elided bonds.}
    \label{fig:selection-and-deselection}
\end{figure}

@@
